Qualifying Report

### 2018-04-30 QualifyingReport/QualifyingReport.tex
added more to overview of problem

\begin{document}
	\maketitle
	\newpage
	\section{Overview of Problem}
	I am interested in whether technology can be used to aid the early diagnosis of dementia specifically by analysing speech and language in a natural environment. As part of this, I am exploring the use of technologies such as the Amazon Echo or Google Home kit to capture speech and language. I am using Natural Language Processing to generate features from the captured speech such that we can categorise people into specific categories and/or predict test results on scores using machine learning.

@@

	\section{Work Plan for the future}

@@

	\subsection{April 2021}
	\section{Provision Table of Contents}
	\subsection{Chapter 1: Introduction}
	\subsection{Chapter 2: Literature Review}
	\subsection{Chapter 3: New theories, Description of experiments}
	\subsection{Chapter 4: Results}
	\subsection{Chapter 5: Discussion}
	\subsection{Chapter 6: Conclusion}
\end{document}

>>>>

\begin{document}
	\maketitle
	\newpage
	\section{Overview of Problem}

	Dementia has been identified as one of those fast growing difficulties facing the world. A recent report suggests that in 2015 there were 46 million people with a diagnosis of dementia and that number is expected to hit 131.5 million by 2050(CITE). The report also states that the worldwide cost of dementia in 2018 is estimated to be in the region of one trillon US dollars.
	\newline
	\par
	A lot of work has gone into language analysis based on clinician diagnosis. This takes the form of tasks such as Free Cued Selective Recall Task, the Boston Cogntive Assessment ,and the Mini Mental State Examination. All of which are quite targeted in the language required of the person being examined. A step towards the ambient detection of AD and/or MCI in population requires that we look for similar features in language used naturally as part of general conversation. Part of this work therefore, is to see whether non prescriptive tasks (that is, tasks that do not have a pre determined right answer), can elicit the same or comparable features in language such that this can be detected ambiently. The next part of this work looks at how technology, particularly the use of smart home devices such as the Amazon Echo and Google Home families of devices. 
	\newline
	\par
	The potential impact of this research is immense. Research has shown (has it?) that early diagnosis of people with AD or MCI improves people's quality of life and can slow the progress of the disease. Equally, early diagnosis can increase the number of research opportunities for understanding the early stages of dementia and how the disease progresses so that more research can be conducted which may, in the future, lead to new treatments and other interventions.

@@

	\section{Work Plan for the future}
	\subsection{Proposed Experiments}

@@

	\section{Provision Table of Contents}
	\subsection{Chapter 1: Introduction}
	\subsection{Chapter 2: Literature Review}
	\subsection{Chapter 3: New theories, Description of experiments}
	\subsection{Chapter 4: Results}
	\subsection{Chapter 5: Discussion}
	\subsection{Chapter 6: Conclusion}
\end{document}
